Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/WSSSPE3_review.tex
Attempt to enrich the abstract.

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage this to happen.
\end{abstract}

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). The report includes a
description of the keynote presentation and a set of lightning talks. It also
focuses on the discussions, future steps, and future organization for a set of
self-organized working groups on topics including developing pathways to funding
scientific software; constructing useful common metrics for crediting software
stakeholders; identifying principles for sustainable software engineering
design; reaching out to research software organizations around the globe; building
communities for software sustainability. For each group, we include a point of
contact and a landing page that can be used by those who want to join that
group's future activities. The main challenge left by the workshop is to see if
the groups will execute these activities that they have scheduled, and how the
WSSSPE community can encourage this to happen.
\end{abstract}
